### 2013-03-13 doc/sosp13/memory.tex
bib for memory consistency model

\paragraph{Memory consistency model discussion} As mentioned earlier, all
synchronization operations are done via delegate operations. Since they all
execute in their home node, they are guaranteed to be serialized , with their
updates visible to all cores across the system in the same order. Also, tasks
are restricted to a single outstanding delegate operation at a time, and
therefore are not subject to potential request reordering. Consequently, all
synchronization operations execute in program order and are made visible in
the same order to all cores in the system. These properties are sufficient to
guarantee a memory model that offers sequential consistency for data-race-free
programs~\cite{drf} (all accesses to shared data are separated by
synchronization). This is the memory model that underpins C/C++.

>>>>

\paragraph{Memory consistency model discussion} As mentioned earlier, all
synchronization operations are done via delegate operations. Since they all
execute in their home node, they are guaranteed to be serialized , with their
updates visible to all cores across the system in the same order. Also, tasks
are restricted to a single outstanding delegate operation at a time, and
therefore are not subject to potential request reordering. Consequently, all
synchronization operations execute in program order and are made visible in
the same order to all cores in the system. These properties are sufficient to
guarantee a memory model that offers sequential consistency for data-race-free
programs~\cite{AdveHill1990} (all accesses to shared data are separated by
synchronization). This is the memory model that underpins C/C++~\cite{N2480,N2800}.
